An evolutionary algorithm\\ for optimization of roll cutting

### 2013-08-09 docs/article_ru.tex
Fix typo in article.
Fix typo in article's list of references.

\begin{abstract}
This paper is concerned with multiobjective problem of optimal roll cutting. 
Important technological limitations imposed on planning process by cutting 
equipment are taken into account with refined formal model. The proposed 
solution method is based on evolutionary computations. The choice of coding 
scheme used to represent solutions in evolutionary algorithm is influenced 
by the combinatorial structure of the original cutting stock problem. 
Combinatorial approach is augmented with adaptive pattern generation in 
implementation of evolutionary operators. A new suite of test problems is 
proposed and used to evaluate performance of the method in computational 
experiments. The results show that the proposed approach is feasible and 
could be adapted to solve cutting stock problems of similar structure.
\smallskip

@@

\bibitem{bib:github} bib:github : EA-based solver for 1.5D MSSCSP [Electronic 
resource]. 
--- 2013. --- [Cited 2013, 1 June]. 
--- Available from : \url{https://bib:github.com/akavrt/csp}.

>>>>

\begin{abstract}
This paper is concerned with multiobjective problem of optimal roll cutting. 
Important technological limitations imposed on planning process by cutting 
equipment are taken into account with refined formal model. The proposed 
solution method is based on evolutionary computation. The choice of coding 
scheme used to represent solutions in evolutionary algorithm is influenced 
by the combinatorial structure of the original cutting stock problem. 
Combinatorial approach is augmented with adaptive pattern generation in 
implementation of evolutionary operators. A new suite of test problems is 
proposed and used to evaluate performance of the method in computational 
experiments. The results show that the proposed approach is feasible and 
could be adapted to solve cutting stock problems of similar structure.
\smallskip

@@

\bibitem{bib:github} GitHub : EA-based solver for 1.5D MSSCSP [Electronic 
resource]. 
--- 2013. --- [Cited 2013, 1 June]. 
--- Available from : \url{https://github.com/akavrt/csp}.
